High-order cognition is supported by complex but compressible brain activity patterns

### 2023-02-27 paper/boneyard.tex
updating figures (captions and layouts)

>>>>

  We also wondered how this compression would change across brain regions.  We repeated the analysis but limited the brain hubs to 7 networks using the Yeo et al. (2011) network parcellation shown here in the inflated brain (Fig.~\ref{fig:decode_pcs_network}, d.). We found that as complexity of the stimuli increases, decoding accuracy increases
  with higher cognitive areas. (Fig.~\ref{fig:decode_pcs_network}).

  % As complexity of the stimuli increases, decoding accuracy increases
  % with higher cognitive areas. (Fig.~\ref{fig: decode_pcs_network}).

  %  If, there is some understanding of the narrative that accumulates over time, we should be able to see that change.

### 2023-02-27 paper/main.tex
updated network figure
updating figures (captions and layouts)

  \caption{\textbf{Decoding accuracy and compression.} \textbf{A. Decoding accuracy by
      number of components.} Ribbons of each color display
    cross-validated decoding performance for each condition (intact,
    paragraph, word, and rest), as a function of the number of components (features) used to
    represent the data.  The horizontal red line denotes chance performance, and the horizontal black
    line denotes 5\% decoding accuracy (used as a reference in Panel B).  \textbf{B. Numbers of components
    required to reach a fixed decoding accuracy threshold, by condition.}  The panel displays a zoomed-in
    view of the inset in Panel A.  Intersections between each condition's decoding accuracy curve
    and the 5\% decoding accuracy reference line are marked by arrows.  \textbf{C. Estimating
    inflection points.}  We sought to identify an ``inflection point'' for each decoding curve, denoting
    the number of components at which the decoding curve asymptotes.  We fit sigmoid functions to each
    decoding curve (left sub-panel) and then computed the minimum number of components where the
    second derivative of the sigmoid was both positive and less than a threshold value of 0.0001.
    \textbf{D. Inflection points by condition.}  Each dot displays the number of components ($x$-axis)
    and decoding accuracy ($y$-axis) at one condition's inflection point.}

    \label{fig:decoding-inflection}
  \end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/decode_pcs_network.pdf}
  \caption{\textbf{Inflection points by network.} \textbf{a.}
    Inflection point was calculated as explained in
    Fig.~\ref{fig:decode_interpret}, b. Analyses were limited by the
    brain networks (using the \cite{YeoEtal11} network parcellation) and
    arranged in increasing order relative to the intact condition.
    \textbf{b. and c.} For the total time in the intact condition, we are plotting the relative inflection points (\textbf{b.}) and corresponding number of components (\textbf{c.}) by network. \textbf{d.} The network parcellation defined by \cite{YeoEtal11} is displayed on the inflated brain maps. The colors and network labels serve as a legend for \textbf{a.} and \textbf{d.}}
  \label{fig:decode_pcs_network}
\end{figure}

We also wondered how this compression would change across brain regions.  We repeated the analysis but limited the brain hubs to 7 networks using the Yeo et al. (2011) network parcellation shown here in the inflated brain (Fig.~\ref{fig:decode_pcs_network}, d.). We found that as complexity of the stimuli increases, decoding accuracy increases
with higher cognitive areas. (Fig.~\ref{fig:decode_pcs_network}).

% As complexity of the stimuli increases, decoding accuracy increases
% with higher cognitive areas. (Fig.~\ref{fig: decode_pcs_network}).

%  If, there is some understanding of the narrative that accumulates over time, we should be able to see that change.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/decode_pcs.pdf}
  \caption{\textbf{Inflection points by thirds.} \textbf{a.}
    Decoding accuracy by number of components not broken into thirds
    (Fig.~\ref{fig:decode_interpret} a.). \textbf{b. and c.}
    Quantifying changes in decoding accuracy across
time. \textbf{b.} Slope of decoding accuracy was calculated by fitting
a regression line for each component/condition for each
third. \textbf{c.}  We also repeated the analysis
(Fig.~\ref{fig:decode_interpret}, b.) to obtain the inflection point
for each condition and for each third. \textbf{d.}  Decoding accuracy by number of components for each third of the scan time. We repeated the same analysis in Fig.~\ref{fig:decode_interpret} a. but breaking the scan time for each condition into 3 intervals.
}
  \label{fig:decode_pcs_thirds}
\end{figure}

>>>>

\caption{\textbf{Decoding accuracy and compression.} \textbf{A. Decoding
accuracy by number of components.} Ribbons of each color display
cross-validated decoding performance for each condition (intact, paragraph,
word, and rest), as a function of the number of components (features) used to
represent the data. The horizontal red line denotes chance performance, and the
horizontal black line denotes 5\% decoding accuracy (used as a reference in
Panel B). \textbf{B. Numbers of components required to reach a fixed decoding
accuracy threshold, by condition.} The panel displays a zoomed-in view of the
inset in Panel A. Intersections between each condition's decoding accuracy
curve and the 5\% decoding accuracy reference line are marked by arrows.
\textbf{C. Estimating inflection points.} We sought to identify an ``inflection
point'' for each decoding curve, denoting the number of components at which the
decoding curve asymptotes. We fit sigmoid functions to each decoding curve
(left sub-panel) and then computed the minimum number of components where the
second derivative of the sigmoid was both positive and less than a threshold
value of 0.0001. \textbf{D. Inflection points by condition.} Each dot displays
the number of components ($x$-axis) and decoding accuracy ($y$-axis) at one
condition's inflection point. All error ribbons denote bootstrap-estimated 95\%
confidence intervals.}

    \label{fig:inflection}
  \end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/decode_pcs_network}

  \caption{\textbf{Network-specific decoding accuracy and compression.}
  \textbf{A. Decoding accuracy and number of components for network-specific
  inflection points.} We considered the seven networks identified by
  \cite{YeoEtal11}. We computed each network's inflection point, for each
  experimental condition, using the procedure described in
  Figure~\ref{fig:inflection}C. \textbf{B. Network-specific decoding
  accuracy.} Each of the seven networks are colored according to the decoding
  accuracy at the network's inflection point for the ``intact'' experimental
  condition (corresponding to the dark blue curve in Panel A). \textbf{C.
  Network-specific compression.} Each of the seven networks are colored
  according to the number of components at the network's inflection point for
  the intact experimental condition. Larger numbers of components reflect lower
  compressibility.}

  \label{fig:networks}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figs/information_and_compression_over_time.pdf}

\caption{\textbf{Changes in decoding accuracy and compression over time.}
\textbf{A. Decoding accuracy by number of components, by story segment.} Each
family of curves is plotted in the same format as Figure~\ref{fig:inflection}A
but reflects data only from one third of the dataset. \textbf{B. Inflection
points by condition and segment.} The dots re-plot the inflection points from
Figure~\ref{fig:inflection}D for reference. The numbers denote the inflection
points for each third of the dataset (1: first third; 2: second third; 3: third
third; colors denote experimental conditions). \textbf{C. Change in decoding
accuracy over time, by number of components.} For each number of components
($x$-axis) and condition (color), we fit a regression line to the decoding
accuracies obtained for the first, second, and third thirds of the dataset
(corresponding to the left, middle, and right columns of Panel A,
respectively). The $y$-axis denotes the slopes of the regression lines. All
error ribbons denote bootstrap-estimated 95\% confidence intervals.}

\label{fig:inflection-thirds}

\end{figure}
